Trajipaq_sentiment_cr

### 2023-08-10 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
update pays/origine
update origine

trajipaq <- merge(trajipaq, pays, by.x = "Q11",
                by.y = "Country Name", all.x = TRUE)

trajipaq <-
  trajipaq %>%
  mutate(origine = Region)

>>>>

pays <-
  pays %>%
    mutate(Country = recode(Country,
                            "Russie" = "Russie, Fédération de",
                            "Congo (Kinshasa)" = "Congo, République démocratique du",
                            "Congo (Brazzaville)" = "Congo, République du",
                            "République dominicaine" = "Dominicaine, République",
                            "République centrafricaine" = "Centrafricaine, République",
                            "Afrique du Sud" = "Afrique du Sud, République d'"
  ))

trajipaq <- merge(trajipaq, pays, by.x = "Q11",
                by.y = "Country", all.x = TRUE)
trajipaq <-
  trajipaq %>%
  mutate(origine = Region)
